---
title: "Homework_5"
author: "Caitlyn Bruntz"
date: "2023-03-01"
output: html_document
---

# Names of all team members: Angelina Allen and Caitlyn Bruntz
# Link to github repository: https://github.com/cmbruntz/Homework-5.git
# Paragraph commenting on workflow: 

```{r}
library(ggplot2)
df = read.csv("https://ds202-at-isu.github.io/labs/data/choco.csv")
head(df)
colnames(df)
str(df)
```
# What is the overall number of chocolate bars rated?

```{r}
nrow(choco)
```
*I just looked up how many rows are in this data frame to see how many bars were in here that are rated. So, the answer is 1,852 bars are rated.*

# How does the number of ratings depend on the year? Draw a bar chart of the number of reports.

```{r, warning=FALSE}
ggplot(choco, aes(x = Review.Date)) + geom_bar()
```


# How are ratings distributed
```{r}
histogram
```


# Do ratings depend on the cocoa percentage of a chocolate bar?
```{r}
scatterplot
```


#How do ratings comopare across different company locations?
```{r}
locations = dplyr::filter(df, Company.Location %in% c("U.S.A.", "France", "Canada"))
barchart
```



