---
title: "Homework_5"
author: "Caitlyn Bruntz"
date: "2023-03-01"
output: html_document
---

# Names of all team members: Angelina Allen and Caitlyn Bruntz
# Link to github repository: https://github.com/cmbruntz/Homework-5.git
# Paragraph commenting on workflow: 

```{r}
library(ggplot2)
choco = read.csv("https://ds202-at-isu.github.io/labs/data/choco.csv")
head(choco)
colnames(choco)
str(choco)
```

# What is the overall number of chocolate bars rated?

```{r}
nrow(choco)
```
*I just looked up how many rows are in this data frame to see how many bars were in here that are rated. So, the answer is 1,852 bars are rated.*

# How does the number of ratings depend on the year? Draw a bar chart of the number of reports.

```{r, warning=FALSE}
ggplot(choco, aes(x = Review.Date)) + geom_bar()
```


# How are ratings distributed?
 # The ratings are distributed in a fairly normal distribution. However, there are outliers in both directions.
```{r}

choco$rating.numeric = as.numeric(choco$Rating)
levels(choco$rating.numeric)

distribution = ggplot(choco, aes(x = rating.numeric)) + 
  geom_histogram() +
  ggtitle("Rating Distribution")
distribution
```


# Do ratings depend on the cocoa percentage of a chocolate bar?

```{r}
scatter = ggplot(choco, aes(x = Cocoa.Pct, y = Rating))+ geom_point()
scatter
```


#How do ratings compare across different company locations?

```{r}
choco$CL.factor = as.factor(choco$Company.Location)
str(choco)

choco1 = dplyr::filter(choco, CL.factor %in% c("U.S.A.", "France", "Canada"))

box = ggplot(choco1, aes(x = CL.factor, y = Rating)) +
  geom_boxplot() + facet_wrap(~CL.factor)
box
```

#Question 3: What company has the highest ratings?
#Top 3 companies are in side-by-side boxplots
 # Tobago Estate consistently had a four rating. Ocelot and Heirloom Cacao Preservation both had a mean rating of 3.875 and a range of 3.75-4.

```{r}
choco$c.factor = as.factor(choco$Company)
str(choco)
levels(reorder(choco$c.factor, choco$Rating, na.rm = TRUE))

choco2 = dplyr::filter(choco, c.factor %in% c("Heirloom Cacao Preservation (Zokoko)", "Ocelot", "Tobago Estate (Pralus)"))
choco2

box = ggplot(choco2, aes(x = c.factor, y = Rating)) +
  geom_boxplot() + facet_wrap(~c.factor)
box
```

#What location has the most number of the best chocolate based off of specific cocoa percentage and rating.  
```{r}
choco1 <- choco %>% select(Rating, Cocoa.Pct, Company.Location)
head(choco1)

best.choco <- choco1 %>% filter(Cocoa.Pct >= '75%', Rating >= 3.5)
View(best.choco)

ggplot(best.choco, aes(x = Company.Location)) + geom_bar()+ coord_flip()
```

